---
title: "data_visualization"
author: "Michelle Johnson"
date: "2023-10-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
```

## setup functions and definitions

Basic/Helper Functions
```{r}
cbFun <- c("#ff107f", "#66b9e8", "#117733", "#c77cff", "#f2b822", "#FFEA7C")

windowsFonts("Arial" = windowsFont("Arial"))

getAdultData <- function(fileName){
  full_name = paste(fileName, "_adults.csv", sep = "")
  print(full_name)
  read.csv(full_name) %>%
    select(-X) %>%
    filter(Generation != "Generation") %>%
    transform(Count = as.numeric(Count), Generation = as.numeric(Generation))
}

getAlleleData <- function(fileName){
  full_name = paste(fileName, "_NEWallele.csv", sep = "")
  print(full_name)
  read.csv(full_name) %>%
    select(-X) %>%
    filter(Generation != "Generation") %>%
    transform(Count = as.numeric(Count), Generation = as.numeric(Generation))
}

getTotalData <- function(fileName){
  full_name = paste(fileName, "_total.csv", sep = "")
  print(full_name)
  read.csv(full_name) %>%
    select(-X) %>%
    filter(Generation != "Generation") %>%
    transform(Count = as.numeric(Count), Generation = as.numeric(Generation))
}

clean_replacement <- function(dataset, number_partners) {
  dataset %>%
    separate(Run, c(NA, NA, "fitCost", NA, "introF", "Run"), sep = "_", remove = T) %>%
    mutate(numPartners = number_partners)
} 

clean_sterility <- function(dataset, number_partners) {
  dataset %>%
    separate(Run, c(NA, NA, "mcProb", NA, "fitCost", "Run"), sep = "_", remove = T) %>%
    mutate(numPartners = number_partners)
} 
```

More complex functions
```{r}
get_replacement_data <- function(oneP_fn, fiveP_fn, twentyP_fn){
  # get total data for each type
  total_replacement_one <- getTotalData(oneP_fn) %>% clean_replacement(., number_partners = 1)
  total_replacement_five <- getTotalData(fiveP_fn) %>% clean_replacement(., number_partners = 5)
  total_replacement_twenty <- getTotalData(twentyP_fn) %>% clean_replacement(., number_partners = 20)
  # combine total data and make sexless
  total_replacement <- rbind(total_replacement_one, total_replacement_five, total_replacement_twenty) %>%
    group_by(Generation, fitCost, introF, Run, numPartners) %>%
    summarise(Count = sum(Count))
  
  #get allele data for each type
  allele_replacement_one <- getAlleleData(oneP_fn) %>% clean_replacement(number_partners = 1)
  allele_replacement_five <- getAlleleData(fiveP_fn) %>% clean_replacement(number_partners = 5)
  allele_replacement_twenty <- getAlleleData(twentyP_fn) %>% clean_replacement(number_partners = 20)
  # combine allele data and make sexless
  allele_replacement <- rbind(allele_replacement_one, allele_replacement_five, allele_replacement_twenty) %>% 
    group_by(Generation, fitCost, introF, Allele, Run, numPartners) %>%
    summarise(Allele_Count = sum(Count))
  
  merge(total_replacement, allele_replacement)
}

plot_replacement_data <- function(dataset){
  plot <- dataset %>%
    filter(Allele == "V") %>%
    #filter(introF == 0.1) %>%
    filter(fitCost != 0.4, fitCost != 0.2) %>%
    mutate(percentage = Allele_Count / (2*Count)) %>%
    group_by(Generation, fitCost, introF, numPartners, Allele) %>%
    summarise(avg_percentage = mean(percentage)) %>%
    filter(avg_percentage != 0) %>%
    ggplot(aes(x = Generation, y = avg_percentage, group = fitCost, color = fitCost,
               fill = fitCost)) +
    geom_line(size = 0.8) +
    scale_linetype_binned() +
    facet_wrap(~numPartners, ncol = 3, 
               labeller = as_labeller(c(`1` = "One Partner",
                                        `5` = "Five Partners",
                                        `20` = "Twenty Partners"))) +
    theme_light() +
    ylab("Percent ClvR") +
    labs(color = "Fitness Cost") +
    scale_colour_manual(values = cbFun) +
    scale_fill_manual(values = cbFun)
    
  fullPlot <- plot +
    theme(
      strip.background = element_rect(
      color=NULL, fill=NULL, size=0, linetype="blank"),
      #strip.text.x = element_text(angle = 0, hjust = 0),
      text = element_text(size = 10, family = "Arial"))
  
  fullPlot
}

get_suppression_data <- function(oneP_fn, fiveP_fn, twentyP_fn){
  # collect all the data
  total_fsterile_one <- getTotalData(oneP_fn) %>%
    clean_sterility(., number_partners = 1)
  
  total_fsterile_five <- getTotalData(fiveP_fn) %>%
    clean_sterility(., number_partners = 5)
  
  total_fsterile_twenty <- getTotalData(twentyP_fn) %>%
    clean_sterility(., number_partners = 20)
  
  total_fsterile <- rbind(total_fsterile_one, total_fsterile_five) %>%
    rbind(., total_fsterile_twenty) %>%
    group_by(Generation, Run, mcProb, fitCost, numPartners) %>%
    summarise(Count = sum(Count))
}

plot_suppression_data <- function(dataset){
  female_plot <- dataset %>%
    filter(fitCost != 0.2) %>%
    filter(mcProb %in% c(0, 0.3)) %>%
    group_by(Generation, mcProb, fitCost, numPartners) %>%
    summarise(avg_Count = mean(Count)) %>% # remove Runs
    ggplot(aes(x = Generation, y = avg_Count, group = interaction(fitCost, mcProb), color = fitCost, linetype = mcProb)) +
    geom_line(size = 0.8) +
    facet_wrap(~numPartners, ncol = 3,
               labeller = as_labeller(c(`1` = "One Partner",
                                        `5` = "Five Partners",
                                        `20` = "Twenty Partners"))) +
    labs(y = "Average Total Population",
         color = "Fitness Cost", 
         linetype = "Maternal \nCarryover") +
    ylim(0, 10000) +
    scale_y_continuous(breaks=c(0, 2500, 5000, 7500, 10000)) +
    theme_light() +
    #xlim(0, 30) +
    scale_colour_manual(values = cbFun)
    
  female_plot <- female_plot +
    theme(
      strip.background = element_rect(
      color=NULL, fill=NULL, size=0, linetype="blank"),
      strip.text.x = element_text(angle = 0, hjust = 0),
      text = element_text(size = 10, family = "Arial"))
  
  female_plot
}
```


# 10% introduction

get separate panels
```{r}
tenPercent_replacement <- get_replacement_data("final_data/onePartner_haploidFitCosts_noSterile",
                     "final_data/fivePartner_haploidFitCosts_noSterile",
                     "final_data/twentyPartner_haploidFitCosts_noSterile") %>% plot_replacement_data()

tenPercent_replacement

tenPercent_femSterile <- get_suppression_data("final_data/onePartner_female_sterility",
                     "final_data/fivePartner_female_sterility",
                     "final_data/twentyPartner_female_sterility") %>% plot_suppression_data()

tenPercent_femSterile

tenPercent_maleSterile <- get_suppression_data("final_data/onePartner_male_sterility",
                     "final_data/fivePartner_male_sterility",
                     "final_data/twentyPartner_male_sterility") %>% plot_suppression_data()

tenPercent_maleSterile
```

# 20% introduction

get separate panels
```{r}
twentyPercent_replacement <- get_replacement_data("final_data/int20_onePartner_haploidFitCosts_noSterile",
                     "final_data/int20_fivePartner_haploidFitCosts_noSterile",
                     "final_data/int20_twentyPartner_haploidFitCosts_noSterile") %>% plot_replacement_data()

twentyPercent_replacement

twentyPercent_femSterile <- get_suppression_data("final_data/int20_onePartner_female_sterility",
                     "final_data/int20_fivePartner_female_sterility",
                     "final_data/int20_twentyPartner_female_sterility") %>% plot_suppression_data()

twentyPercent_femSterile

twentyPercent_maleSterile <- get_suppression_data("final_data/int20_onePartner_male_sterility",
                     "final_data/int20_fivePartner_male_sterility",
                     "final_data/int20_twentyPartner_male_sterility") %>% plot_suppression_data()

twentyPercent_maleSterile
```


# Replacement - 20% introduction

```{r}
# get sexless total data for each 
total_replacement_one <- getTotalData("final_data/int20_onePartner_haploidFitCosts_noSterile") %>%
  clean_replacement(., number_partners = 1)

total_replacement_five <- getTotalData("final_data/int20_fivePartner_haploidFitCosts_noSterile") %>%
  clean_replacement(number_partners = 5)

total_replacement_twenty <- getTotalData("final_data/int20_twentyPartner_haploidFitCosts_noSterile") %>%
  clean_replacement(number_partners = 20)

# combine and make sexless
total_replacement <- rbind(total_replacement_one, total_replacement_five) %>% 
  rbind(., total_replacement_twenty) %>%
  group_by(Generation, fitCost, introF, Run, numPartners) %>%
  summarise(Count = sum(Count))

# get sexless allele data for each
allele_replacement_one <- getAlleleData("final_data/int20_onePartner_haploidFitCosts_noSterile") %>%
  clean_replacement(number_partners = 1)

allele_replacement_five <- getAlleleData("final_data/int20_fivePartner_haploidFitCosts_noSterile") %>%
  clean_replacement(number_partners = 5)

allele_replacement_twenty <- getAlleleData("final_data/int20_twentyPartner_haploidFitCosts_noSterile") %>%
  clean_replacement(number_partners = 20)

# combine and make sexless
allele_replacement <- rbind(allele_replacement_one, allele_replacement_five) %>% 
  rbind(., allele_replacement_twenty) %>% 
  group_by(Generation, fitCost, introF, Allele, Run, numPartners) %>%
  summarise(Allele_Count = sum(Count))

```

###graph!
```{r}
plot <- allele_replacement %>%
  filter(Allele == "V") %>%
  filter(fitCost != 0.4, fitCost != 0.2) %>%
  merge(., total_replacement) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, fitCost, introF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  filter(avg_percentage != 0) %>%
  ggplot(aes(x = Generation, y = avg_percentage, group = fitCost, color = fitCost,
             fill = fitCost)) +
  geom_line(size = 0.8) +
  scale_linetype_binned() +
  facet_wrap(~numPartners, ncol = 3, 
             labeller = as_labeller(c(`1` = "One Partner",
                                      `5` = "Five Partners",
                                      `20` = "Twenty Partners"))) +
  theme_light() +
  ylab("Percent ClvR") +
  labs(color = "Fitness Cost") +
  scale_colour_manual(values = cbFun) +
  scale_fill_manual(values = cbFun)
  
fullPlot <- plot +
  theme(
    strip.background = element_rect(
    color=NULL, fill=NULL, size=0, linetype="blank"),
    #strip.text.x = element_text(angle = 0, hjust = 0),
    text = element_text(size = 10, family = "Arial"))

fullPlot
```

# Females homozygous sterile - 20% introduction
```{r}
total_fsterile_one <- getTotalData("final_data/int20_onePartner_female_sterility") %>%
  clean_sterility(., number_partners = 1)

total_fsterile_five <- getTotalData("final_data/int20_fivePartner_female_sterility") %>%
  clean_sterility(., number_partners = 5)

total_fsterile_twenty <- getTotalData("final_data/int20_twentyPartner_female_sterility") %>%
  clean_sterility(., number_partners = 20)

total_fsterile <- rbind(total_fsterile_one, total_fsterile_five) %>%
  rbind(., total_fsterile_twenty) %>%
  group_by(Generation, Run, mcProb, fitCost, numPartners) %>%
  summarise(Count = sum(Count))
  
```

### graph data
```{r}
total_fsterile %>% 
  ggplot(aes(x = Generation, y = Count, group = interaction(fitCost, Run), color = fitCost)) +
  geom_line() +
  facet_grid(mcProb ~ numPartners) +
  xlim(0, 50)

female_plot <- total_fsterile %>%
  filter(fitCost != 0.2) %>%
  filter(mcProb %in% c(0, 0.3)) %>%
  group_by(Generation, mcProb, fitCost, numPartners) %>%
  summarise(avg_Count = mean(Count)) %>% # remove Runs
  ggplot(aes(x = Generation, y = avg_Count, group = interaction(fitCost, mcProb), color = fitCost, linetype = mcProb)) +
  geom_line(size = 0.8) +
  facet_wrap(~numPartners, ncol = 3,
             labeller = as_labeller(c(`1` = "One Partner",
                                      `5` = "Five Partners",
                                      `20` = "Twenty Partners"))) +
  labs(y = "Average Total Population",
       color = "Fitness Cost", 
       linetype = "Maternal \nCarryover") +
  ylim(0, 10000) +
  scale_y_continuous(breaks=c(0, 2500, 5000, 7500, 10000)) +
  theme_light() +
  #xlim(0, 30) +
  scale_colour_manual(values = cbFun)
  
female_plot <- female_plot +
  theme(
    strip.background = element_rect(
    color=NULL, fill=NULL, size=0, linetype="blank"),
    strip.text.x = element_text(angle = 0, hjust = 0),
    text = element_text(size = 10, family = "Arial"))

female_plot
```

# Males homozygous sterile - 20% introduction
```{r}

total_msterile_one <- getTotalData("final_data/int20_onePartner_male_sterility") %>%
  clean_sterility(., number_partners = 1)

total_msterile_five <- getTotalData("final_data/int20_fivePartner_male_sterility") %>%
  clean_sterility(., number_partners = 5)

total_msterile_twenty <- getTotalData("final_data/int20_twentyPartner_male_sterility") %>%
  clean_sterility(., number_partners = 20)

total_msterile <- rbind(total_msterile_one, total_msterile_five) %>%
  rbind(., total_msterile_twenty) %>%
  group_by(Generation, Run, mcProb, fitCost, numPartners) %>%
  summarise(Count = sum(Count))
  
```

### graph data
```{r}
male_plot <- total_msterile %>%
  filter(fitCost != 0.2) %>%
  filter(mcProb %in% c(0, 0.3)) %>%
  group_by(Generation, mcProb, fitCost, numPartners) %>%
  summarise(avg_Count = mean(Count)) %>% # remove Runs
  ggplot(aes(x = Generation, y = avg_Count, group = interaction(fitCost, mcProb), color = fitCost, linetype = mcProb)) +
  geom_line(size = 0.8) +
  facet_wrap(~numPartners, ncol = 3,
             labeller = as_labeller(c(`1` = "One Partner",
                                      `5` = "Five Partners",
                                      `20` = "Twenty Partners"))) +
  labs(y = "Average Total Population",
       color = "Fitness Cost", 
       linetype = "Maternal \nCarryover") +
  ylim(0, 10000) +
  scale_y_continuous(breaks=c(0, 2500, 5000, 7500, 10000)) +
  theme_light() +
  #xlim(0, 30) +
  scale_colour_manual(values = cbFun)
  
male_plot <- male_plot +
  theme(
    strip.background = element_rect(
    color=NULL, fill=NULL, size=0, linetype="blank"),
    strip.text.x = element_text(angle = 0, hjust = 0),
    text = element_text(size = 10, family = "Arial"))

male_plot
```

# Resistant Mutations
## Modification

Write functions! to reduce clutter later
```{r}
get_RM_data <- function(noRM_fn, RM_fn, noRM_fn_label, RM_fn_label) {
  # pull total data
  total_replacement_noRM <- getTotalData(noRM_fn) %>%
     clean_replacement(., number_partners = noRM_fn_label)
  total_replacement_RM <- getTotalData(RM_fn) %>%
     clean_replacement(., number_partners = RM_fn_label)
  # combine and desex
  total_replacement <- rbind(total_replacement_noRM, total_replacement_RM) %>% 
    group_by(Generation, fitCost, introF, Run, numPartners) %>%
    summarise(Count = sum(Count))
  # pull allele data
  allele_replacement_noRM <- getAlleleData(noRM_fn) %>%
    clean_replacement(number_partners = noRM_fn_label)
  allele_replacement_RM <- getAlleleData(RM_fn) %>%
    clean_replacement(number_partners = RM_fn_label)
  # combine and desex
  allele_replacement <- rbind(allele_replacement_noRM, allele_replacement_RM) %>%
    group_by(Generation, fitCost, introF, Allele, Run, numPartners) %>%
    summarise(Allele_Count = sum(Count))
  merge(allele_replacement, total_replacement)
}

plot_RM_data <- function(dataset){
  plot <- dataset %>%
    filter(Allele == "V") %>%
    filter(introF == 0.1) %>%
    filter(fitCost != 0.4, fitCost != 0.2) %>%
    mutate(percentage = Allele_Count / (2*Count)) %>%
    group_by(Generation, fitCost, introF, numPartners, Allele) %>%
    summarise(avg_percentage = mean(percentage)) %>%
    filter(avg_percentage != 0) %>%
    ggplot(aes(x = Generation, y = avg_percentage, group = fitCost, color = fitCost,
               fill = fitCost)) +
    geom_line(size = 0.8) +
    scale_linetype_binned() +
    facet_wrap(~numPartners, ncol = 3) + #, 
               #labeller = as_labeller(c(`1` = "One Partner",
              #                          `5` = "Five Partners",
              #                          `20` = "Twenty Partners"))) +
    theme_light() +
    ylab("Percent ClvR") +
    labs(color = "Fitness Cost") +
    scale_colour_manual(values = cbFun) +
    scale_fill_manual(values = cbFun) + xlim(NA, 20)
  
  plot +
  theme(
    strip.background = element_rect(
    color=NULL, fill=NULL, size=0, linetype="blank"),
    #strip.text.x = element_text(angle = 0, hjust = 0),
    text = element_text(size = 10, family = "Arial"))
}
```


Get one partner, five partner, and twenty partner RM
```{r}
new_attempt <- get_RM_data(
  "final_data/onePartner_haploidFitCosts_noSterile",
  "12-15/mutation_data/resistant_modification_onePartner_haploidFitCosts_noSterile",
  "one partner no RM",
  "one partner with RM")

plot_RM_data(new_attempt)

get_RM_data(
  "final_data/fivePartner_haploidFitCosts_noSterile",
  "12-15/mutation_data/resistant_modification_fivePartner_haploidFitCosts_noSterile",
  "five partner no RM",
  "five partner with RM") %>% plot_RM_data()

get_RM_data(
  "final_data/twentyPartner_haploidFitCosts_noSterile",
  "12-15/mutation_data/resistant_modification_twentyPartner_haploidFitCosts_noSterile",
  "twenty partner no RM",
  "twenty partner with RM") %>% plot_RM_data()

RM_manyPercents <- get_RM_data(
  "final_data/onePartner_haploidFitCosts_noSterile",
  "12-15/mutation_data/RM_manypercents_onePartner_haploidFitCosts_noSterile",
  "no RM",
  "RM, 20% resistant")

plot <- RM_manyPercents %>%
    filter(Allele == "C") %>%
    filter((fitCost < 0.2) | (numPartners == "RM, 20% resistant")) %>%
    mutate(percentage = Allele_Count / (2*Count)) %>%
    group_by(Generation, fitCost, introF, numPartners, Allele) %>%
    summarise(avg_percentage = mean(percentage)) %>%
    filter(avg_percentage != 0) %>%
    ggplot(aes(x = Generation, y = avg_percentage, group = fitCost, color = fitCost,
               fill = fitCost)) +
    geom_line(size = 0.8) +
    scale_linetype_binned() +
    facet_wrap(~numPartners, ncol = 3) + #, 
               #labeller = as_labeller(c(`1` = "One Partner",
              #                          `5` = "Five Partners",
              #                          `20` = "Twenty Partners"))) +
    theme_light() +
    ylab("Percent Cleaved Target") +
    labs(color = "Fitness Cost") +
    scale_colour_manual(values = cbFun) +
    scale_fill_manual(values = cbFun) + xlim(NA, 20)
  
plot +
  theme(
    strip.background = element_rect(
    color=NULL, fill=NULL, size=0, linetype="blank"),
    #strip.text.x = element_text(angle = 0, hjust = 0),
    text = element_text(size = 10, family = "Arial"))

RM_manyPercents %>%
    filter((fitCost < 0.2) | (numPartners == "RM, 20% resistant")) %>%
    mutate(percentage = Allele_Count / (2*Count)) %>%
    group_by(Generation, fitCost, introF, numPartners, Allele) %>%
    summarise(avg_percentage = mean(percentage)) %>%
    filter(avg_percentage != 0) %>%
    ggplot(aes(x = Generation, y = avg_percentage, group = fitCost, color = fitCost,
               fill = fitCost)) +
    geom_line(size = 0.8) +
    scale_linetype_binned() +
    facet_grid(numPartners~Allele) + #, 
               #labeller = as_labeller(c(`1` = "One Partner",
              #                          `5` = "Five Partners",
              #                          `20` = "Twenty Partners"))) +
    theme_light() +
    ylab("Percent ClvR") +
    labs(color = "Fitness Cost") +
    scale_colour_manual(values = cbFun) +
    scale_fill_manual(values = cbFun) + xlim(NA, 20)

```


One Partner RM, but for Diploid vs. Haploid vs. Haploid&Diploid fitness costs
```{r}
fig <- get_RM_data(
  "final_data/onePartner_haploidFitCosts_noSterile",
  "12-15/mutation_data/resistant_modification_onePartner_haploidFitCosts_noSterile",
  "no RM, one partner",
  "20% RM, one partner. Haploid FC") %>%
  filter(Allele == "V") %>%
  filter(fitCost != 0.4, fitCost != 0.2) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, fitCost, introF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  filter(avg_percentage != 0) %>%
  ggplot(aes(x = Generation, y = avg_percentage, group = fitCost, color = fitCost,
             fill = fitCost)) +
  geom_line(size = 0.8) +
  scale_linetype_binned() +
  facet_wrap(~numPartners, ncol = 3) + #, 
             #labeller = as_labeller(c(`1` = "One Partner",
            #                          `5` = "Five Partners",
            #                          `20` = "Twenty Partners"))) +
  theme_light() +
  ylab("Percent ClvR") +
  labs(color = "Fitness Cost") +
  scale_colour_manual(values = cbFun) +
  scale_fill_manual(values = cbFun) + xlim(NA, 40)
fig

fig <- get_RM_data(
  "1-4/RM_manypercents_onePartner_diploidFitCosts_noSterile",
  "1-4/RM_manypercents_onePartner_diploidHaploidFitCosts_noSterile",
  "20% RM, Diploid FC",
  "20% RM, Diploid and Haploid FC") %>%
  filter(Allele == "V") %>%
  filter(fitCost != 0.4, fitCost != 0.2) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, fitCost, introF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  filter(avg_percentage != 0) %>%
  ggplot(aes(x = Generation, y = avg_percentage, group = fitCost, color = fitCost,
             fill = fitCost)) +
  geom_line(size = 0.8) +
  scale_linetype_binned() +
  facet_wrap(~numPartners, ncol = 3) + #, 
             #labeller = as_labeller(c(`1` = "One Partner",
            #                          `5` = "Five Partners",
            #                          `20` = "Twenty Partners"))) +
  theme_light() +
  ylab("Percent ClvR") +
  labs(color = "Fitness Cost") +
  scale_colour_manual(values = cbFun) +
  scale_fill_manual(values = cbFun) + xlim(NA, 40)
fig
```

5p, of above
```{r}
fig <- get_RM_data(
  "final_data/fivePartner_haploidFitCosts_noSterile",
  "1-4/RM_manypercents_fivePartner_haploidFitCosts_noSterile2",
  "no RM, five partner",
  "20% RM, five partner. Haploid FC") %>%
  filter(Allele == "V") %>%
  filter(ifelse(numPartners == "20% RM, five partner. Haploid FC", introF == 0.2, TRUE)) %>%
  filter(fitCost != 0.4, fitCost != 0.2) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, fitCost, introF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  filter(avg_percentage != 0) %>%
  ggplot(aes(x = Generation, y = avg_percentage, group = fitCost, color = fitCost,
             fill = fitCost)) +
  geom_line(size = 0.8) +
  scale_linetype_binned() +
  facet_wrap(~numPartners, ncol = 3) + #, 
             #labeller = as_labeller(c(`1` = "One Partner",
            #                          `5` = "Five Partners",
            #                          `20` = "Twenty Partners"))) +
  theme_light() +
  ylab("Percent ClvR") +
  labs(color = "Fitness Cost") +
  scale_colour_manual(values = cbFun) +
  scale_fill_manual(values = cbFun) + xlim(NA, 40)
fig

fig <- get_RM_data(
  "1-4/RM_manypercents_fivePartner_diploidFitCosts_noSterile",
  "1-4/RM_manypercents_fivePartner_diploidHaploidFitCosts_noSterile",
  "20% RM, Diploid FC",
  "20% RM, Diploid and Haploid FC") %>%
  filter(Allele == "V") %>% filter(introF == 0.2) %>%
  filter(fitCost != 0.4, fitCost != 0.2) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, fitCost, introF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  filter(avg_percentage != 0) %>%
  ggplot(aes(x = Generation, y = avg_percentage, group = fitCost, color = fitCost,
             fill = fitCost)) +
  geom_line(size = 0.8) +
  scale_linetype_binned() +
  facet_wrap(~numPartners, ncol = 3) + #, 
             #labeller = as_labeller(c(`1` = "One Partner",
            #                          `5` = "Five Partners",
            #                          `20` = "Twenty Partners"))) +
  theme_light() +
  ylab("Percent ClvR") +
  labs(color = "Fitness Cost") +
  scale_colour_manual(values = cbFun) +
  scale_fill_manual(values = cbFun) + xlim(NA, 40)
fig
```



## Suppression

### Female Sterility

Write functions, to reduce clutter
```{r}
get_RS_data <- function(noRS_fn, RS_fn, noRS_fn_label, RS_fn_label) {
  # pull total data
  total_replacement_noRS <- getTotalData(noRS_fn) %>%
     clean_sterility(., number_partners = noRS_fn_label)
  total_replacement_RS <- getTotalData(RS_fn) %>%
     clean_sterility(., number_partners = RS_fn_label)
  # combine and desex
  total_replacement <- rbind(total_replacement_noRS, total_replacement_RS) %>% 
    group_by(Generation, Run, mcProb, fitCost, numPartners) %>%
    summarise(Count = sum(Count))
}

graph_RS_data <- function(dataset) {
  female_plot <- dataset %>%
  filter(fitCost != 0.2) %>%
  filter(mcProb %in% c(0, 0.3)) %>%
  group_by(Generation, mcProb, fitCost, numPartners) %>%
  summarise(avg_Count = mean(Count)) %>% # remove Runs
  ggplot(aes(x = Generation, y = avg_Count, group = interaction(fitCost, mcProb), color = fitCost, linetype = mcProb)) +
  geom_line(size = 0.8) +
  facet_wrap(~numPartners, ncol = 3) + #,
             #labeller = as_labeller(c(`1` = "One Partner",
            #                          `5` = "Five Partners",
            #                          `20` = "Twenty Partners"))) +
  labs(y = "Average Total Population",
       color = "Fitness Cost", 
       linetype = "Maternal \nCarryover") +
  ylim(0, 10000) +
  scale_y_continuous(breaks=c(0, 2500, 5000, 7500, 10000)) +
  theme_light() +
  #xlim(0, 30) +
  scale_colour_manual(values = cbFun)
  
female_plot <- female_plot +
  theme(
    strip.background = element_rect(
    color=NULL, fill=NULL, size=0, linetype="blank"),
    strip.text.x = element_text(angle = 0, hjust = 0),
    text = element_text(size = 10, family = "Arial"))

female_plot
}
```


Retrieve and Graph Data
```{r}
get_RS_data("final_data/onePartner_female_sterility",
            "12-15/mutation_data/resistant_suppression_onePartner_femSterile",
            "1p no RS",
            "1p resistant") %>% graph_RS_data() + labs(title = "10% clvr, resistant 5%")

get_RS_data("final_data/onePartner_male_sterility",
            "12-15/mutation_data/resistant_suppression_onePartner_maleSterile",
            "1p no RS",
            "1p resistant") %>% graph_RS_data() + labs(title = "MALES")


get_RS_data("final_data/onePartner_male_sterility",
            "12-15/mutation_data/RS_1percent_onePartner_femSterile",
            "1p no RS",
            "1p resistant") %>% graph_RS_data() + labs(title = "Females, 1%")

get_RS_data("final_data/onePartner_male_sterility",
            "12-15/mutation_data/RS_05percent_onePartner_femSterile",
            "1p no RS",
            "1p resistant") %>% graph_RS_data() + labs(title = "Females, 0.5%")

get_RS_data("final_data/int20_onePartner_male_sterility",
            "12-15/mutation_data/int20_resistant_suppression_onePartner_femSterile",
            "1p no RS",
            "1p resistant") %>% graph_RS_data() + labs(title = "20% clvr, resistant 5%")

```

EXPLORATORY ANALYSIS
```{r}
allele_fsterile_one <- getAlleleData("12-15/mutation_data/resistant_suppression_onePartner_femSterile") %>%
  clean_sterility(., number_partners = 1)

allele_fsterile_one %>% filter(fitCost == 0, mcProb == 0, Run == 1) %>%
  ggplot(aes(x = Generation, y = Count, group = interaction(Sex, Run), color = Sex)) +
  geom_line() +
  facet_wrap(~Allele) + xlim(0, 30) + labs(title = "Run 1")
allele_fsterile_one %>% filter(fitCost == 0, mcProb == 0, Run == 2) %>%
  ggplot(aes(x = Generation, y = Count, group = interaction(Sex, Run), color = Sex)) +
  geom_line() +
  facet_wrap(~Allele) + xlim(0, 30) + labs(title = "Run 2")
allele_fsterile_one %>% filter(fitCost == 0, mcProb == 0, Run == 3) %>%
  ggplot(aes(x = Generation, y = Count, group = interaction(Sex, Run), color = Sex)) +
  geom_line() +
  facet_wrap(~Allele) + xlim(0, 30) + labs(title = "Run 3")

total_fsterile_one <- getTotalData("12-15/mutation_data/resistant_suppression_onePartner_femSterile") %>%
  clean_sterility(., number_partners = 1)

total_fsterile_one %>%
  filter(fitCost == 0, mcProb == 0) %>%
  group_by(Generation, Run, mcProb, fitCost, numPartners) %>%
  summarise(Count = sum(Count)) %>% # desexed
  ggplot(aes(x = Generation, y = Count, group = interaction(fitCost, mcProb), color = fitCost, linetype = mcProb)) +
  geom_line(size = 0.8) +
  facet_wrap(~Run)
  
```

# LOF Clvr

## Modification

## Suppression

### Female & Male Sterility

Get and Graph, using previous RS functions
```{r}
get_RS_data("final_data/onePartner_female_sterility",
            "12-15/mutation_data/lof_clvr_suppression_onePartner_femSterile",
            "1: no lof",
            "1: lof clvr") %>%
  graph_RS_data()

get_RS_data("final_data/fivePartner_female_sterility",
            "12-15/mutation_data/lof_clvr_suppression_fivePartner_femSterile",
            "5: no lof",
            "5: lof clvr") %>%
  graph_RS_data()

get_RS_data("final_data/twentyPartner_female_sterility",
            "12-15/mutation_data/lof_clvr_suppression_twentyPartner_femSterile",
            "20: no lof",
            "20: lof clvr") %>%
  graph_RS_data()

get_RS_data("final_data/onePartner_male_sterility",
            "12-15/mutation_data/lof_clvr_suppression_onePartner_maleSterile",
            "1: no lof",
            "1: lof clvr") %>%
  graph_RS_data() + labs(title = "Male Sterility")

get_RS_data("final_data/fivePartner_male_sterility",
            "12-15/mutation_data/lof_clvr_suppression_fivePartner_maleSterile",
            "5: no lof",
            "5: lof clvr") %>%
  graph_RS_data() + labs(title = "Male Sterility")

get_RS_data("final_data/twentyPartner_male_sterility",
            "12-15/mutation_data/lof_clvr_suppression_twentyPartner_maleSterile",
            "20: no lof",
            "20: lof clvr") %>%
  graph_RS_data() + labs(title = "Male Sterility")
```

Exploration - something weird with males
```{r}
lof_1pmaleA <- getAlleleData("12-15/mutation_data/lof_clvr_suppression_fivePartner_maleSterile") %>%
  clean_sterility(., number_partners = "5: lof clvr")

lof_1pmaleA %>%
  filter(mcProb == 0, fitCost == 0) %>%
  group_by(Generation, Allele, Run, numPartners) %>%
  summarize(Count = sum(Count)) %>%
  ggplot(aes(x = Generation, y = Count, group = Run)) +
  geom_line() + facet_wrap(~Allele)

lof_1pmaleA %>%
  filter(mcProb == 0, fitCost == 0, Sex == "Female") %>%
  ggplot(aes(x = Generation, y = Count, group = Run)) +
  geom_line() + facet_wrap(~Allele) + labs(title = "female sterile")

lof_1pmaleA %>%
  filter(mcProb == 0, fitCost == 0, Sex == "Male") %>%
  ggplot(aes(x = Generation, y = Count, group = Run)) +
  geom_line() + facet_wrap(~Allele) + labs(title = "male sterile")

lof_1pmaleG <- getAdultData("12-15/mutation_data/lof_clvr_suppression_fivePartner_maleSterile") %>%
  clean_sterility(., number_partners = "5: lof clvr")

lof_1pmaleG %>%
  filter(mcProb == 0, fitCost == 0, Sex == "Male", Generation > 30) %>%
  filter(Count != 0) %>%
  ggplot(aes(x = Generation, y = Count, group = Run)) +
  geom_line() + facet_wrap(~Genotype) + labs(title = "males")

lof_1pmaleG %>%
  filter(mcProb == 0, fitCost == 0, Sex == "Female", Generation > 30) %>%
  filter(Count != 0) %>%
  ggplot(aes(x = Generation, y = Count, group = Run)) +
  geom_line() + facet_wrap(~Genotype) + labs(title = "females")
```

Reduced Introduction Frequencies
```{r}
get_RS_data("1-4/lof_clvr_if1_suppression_onePartner_femSterile",
            "12-15/mutation_data/lof_clvr_suppression_onePartner_femSterile",
            "1% LOF clvr",
            "10% LOF clvr") %>%
  graph_RS_data()

get_RS_data("1-4/lof_clvr_if2_suppression_onePartner_femSterile",
            "1-4/lof_clvr_if5_suppression_onePartner_femSterile",
            "2% LOF clvr",
            "5% LOF clvr") %>%
  graph_RS_data()

get_RS_data("1-4/lof_clvr_if2_suppression_fivePartner_femSterile",
            "12-15/mutation_data/lof_clvr_suppression_fivePartner_femSterile",
            "2% LOF clvr",
            "10% LOF clvr") %>%
  graph_RS_data() + labs(title = "5 partner")

get_RS_data("final_data/fivePartner_female_sterility",
            "1-4/lof_clvr_if2_suppression_fivePartner_femSterile",
            "no lof",
            "2% lof clvr") %>%
  graph_RS_data() + labs(title = "5 partner")

get_RS_data("1-4/lof_clvr_if2_suppression_twentyPartner_femSterile",
            "12-15/mutation_data/lof_clvr_suppression_twentyPartner_femSterile",
            "2% LOF clvr",
            "10% LOF clvr") %>%
  graph_RS_data() + labs(title = "20 partner")

get_RS_data("final_data/twentyPartner_female_sterility",
            "1-4/lof_clvr_if2_suppression_twentyPartner_femSterile",
            "no lof",
            "2% lof clvr") %>%
  graph_RS_data() + labs(title = "20 partner")
```

# Recombination distance

Get and Graph, using previous RS functions - one partner
```{r}
fig <- get_RS_data("final_data/onePartner_female_sterility",
            "1-4/rd_1_suppression_onePartner_femSterile",
            "1: no rd",
            "1: 1 rd") %>%
  graph_RS_data()
fig

allele_rd <- getAlleleData("1-4/rd_1_suppression_onePartner_femSterile") %>%
  clean_sterility(., number_partners = 1) %>%
  mutate(Allele = factor(Allele, levels = c("C", "A", "V", "W", "R", "X")))

allele_rd %>% filter(fitCost == 0, mcProb == 0, Run == 1) %>%
  ggplot(aes(x = Generation, y = Count, group = interaction(Sex, Run), color = Sex)) +
  geom_line() +
  facet_wrap(~Allele) + xlim(0, 30) + labs(title = "Run 1")

get_RS_data("final_data/onePartner_female_sterility",
            "1-4/rd_5_suppression_onePartner_femSterile",
            "1: no rd",
            "1: 5 rd") %>%
  graph_RS_data()

fig <- getTotalData("1-4/rd_5_suppression_onePartner_femSterile") %>%
     clean_sterility(., number_partners = "rd 5") %>%
  filter(mcProb %in% c(0, 0.3)) %>%
  group_by(Generation, mcProb, fitCost, Run, numPartners) %>%
  summarize(Count = sum(Count)) %>%
  ggplot(aes(x = Generation, y = Count, group = interaction(fitCost, mcProb, Run), color = fitCost)) +
  geom_line(size = 0.8) +
  facet_wrap(~mcProb, ncol = 3) + #,
             #labeller = as_labeller(c(`1` = "One Partner",
            #                          `5` = "Five Partners",
            #                          `20` = "Twenty Partners"))) +
  labs(y = "Total Population",
       color = "Fitness Cost") +
  ylim(0, 10000) +
  scale_y_continuous(breaks=c(0, 2500, 5000, 7500, 10000)) +
  theme_light() +
  #xlim(0, 30) +
  scale_colour_manual(values = cbFun)
fig

allele_rd <- getAlleleData("1-4/rd_5_suppression_onePartner_femSterile") %>%
  clean_sterility(., number_partners = 1) %>%
  mutate(Allele = factor(Allele, levels = c("C", "A", "V", "W", "R", "X")))

allele_rd %>% filter(fitCost == 0.15, mcProb == 0, Run == 1) %>%
  ggplot(aes(x = Generation, y = Count, group = interaction(Sex, Run), color = Sex)) +
  geom_line() +
  facet_wrap(~Allele) + xlim(0, 50) + labs(title = "Run 1, FC 15%")
```

Five and Twenty Partners
```{r}
fig <- getTotalData("1-4/rd_1_suppression_fivePartner_femSterile") %>%
     clean_sterility(., number_partners = "rd 5") %>%
  filter(mcProb %in% c(0, 0.3)) %>%
  group_by(Generation, mcProb, fitCost, Run, numPartners) %>%
  summarize(Count = sum(Count)) %>%
  ggplot(aes(x = Generation, y = Count, group = interaction(fitCost, mcProb, Run), color = fitCost)) +
  geom_line(size = 0.8) +
  facet_wrap(~mcProb, ncol = 3) + #,
             #labeller = as_labeller(c(`1` = "One Partner",
            #                          `5` = "Five Partners",
            #                          `20` = "Twenty Partners"))) +
  labs(y = "Total Population, 5 partner",
       color = "Fitness Cost") +
  ylim(0, 10000) +
  scale_y_continuous(breaks=c(0, 2500, 5000, 7500, 10000)) +
  theme_light() +
  #xlim(0, 30) +
  scale_colour_manual(values = cbFun)
fig

fig <- getTotalData("1-4/rd_1_suppression_twentyPartner_femSterile") %>%
     clean_sterility(., number_partners = "rd 5") %>%
  filter(mcProb %in% c(0, 0.3)) %>%
  group_by(Generation, mcProb, fitCost, Run, numPartners) %>%
  summarize(Count = sum(Count)) %>%
  ggplot(aes(x = Generation, y = Count, group = interaction(fitCost, mcProb, Run), color = fitCost)) +
  geom_line(size = 0.8) +
  facet_wrap(~mcProb, ncol = 3) + #,
             #labeller = as_labeller(c(`1` = "One Partner",
            #                          `5` = "Five Partners",
            #                          `20` = "Twenty Partners"))) +
  labs(y = "Total Population, 20 partner",
       color = "Fitness Cost") +
  ylim(0, 10000) +
  scale_y_continuous(breaks=c(0, 2500, 5000, 7500, 10000)) +
  theme_light() +
  #xlim(0, 30) +
  scale_colour_manual(values = cbFun)
fig
```


# drive with benefit, vs. drive without benefit, one partner

onePartner_heatmap_fb_drive
onePartner_heatmap_fb_nodrive

```{r}
total_replacement_drive <- getTotalData("12-15/mutation_data/onePartner_heatmap_fb_drive") %>%
  clean_replacement(., number_partners = "drive")

total_replacement_nodrive <- getTotalData("12-15/mutation_data/onePartner_heatmap_fb_nodrive") %>%
  clean_replacement(number_partners = "no drive")

total_replacement_Dnodrive <- getTotalData("12-15/mutation_data/onePartner_heatmap_fb_diploidnodrive") %>%
  clean_replacement(number_partners = "D no drive")

# combine and make sexless
total_replacement <- rbind(total_replacement_drive, total_replacement_nodrive) %>% 
  rbind(., total_replacement_Dnodrive) %>%
  group_by(Generation, fitCost, introF, Run, numPartners) %>%
  summarise(Count = sum(Count)) %>%
  rename(IF = fitCost, FC = introF)

total_replacement

# get sexless allele data for each
allele_replacement_drive <- getAlleleData("12-15/mutation_data/onePartner_heatmap_fb_drive") %>%
  clean_replacement(number_partners = "drive")

allele_replacement_nodrive <- getAlleleData("12-15/mutation_data/onePartner_heatmap_fb_nodrive") %>%
  clean_replacement(number_partners = "no drive")

allele_replacement_Dnodrive <- getAlleleData("12-15/mutation_data/onePartner_heatmap_fb_diploidnodrive") %>%
  clean_replacement(number_partners = "D no drive")

# combine and make sexless
allele_replacement <- rbind(allele_replacement_drive, allele_replacement_nodrive) %>%
  rbind(., allele_replacement_Dnodrive) %>% 
  group_by(Generation, fitCost, introF, Allele, Run, numPartners) %>%
  summarise(Allele_Count = sum(Count)) %>%
  rename(IF = fitCost, FC = introF)

allele_replacement
```

Preliminary graphs
```{r}
allele_replacement %>%
  filter(Allele == "C", numPartners == "drive") %>%
  filter(Generation == 50) %>%
  merge(., total_replacement) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, FC, IF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  ggplot(aes(x = FC, y = IF, fill = avg_percentage)) +
  geom_tile() + labs(title = "percentage at generation 50, with drive")

allele_replacement %>%
  filter(Allele == "C", numPartners == "drive") %>%
  merge(., total_replacement) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  filter(percentage == 1) %>%
  group_by(FC, IF, numPartners, Allele, Run) %>%
  summarise(min_gen = min(Generation)) %>%
  group_by(FC, IF, numPartners, Allele) %>%
  summarise(avg_generation = mean(min_gen)) %>%
  ggplot(aes(x = FC, y = IF, fill = avg_generation)) +
  geom_tile() + labs(title = "fixation time with drive")

allele_replacement %>%
  filter(Allele == "C", numPartners == "no drive") %>%
  filter(Generation == 50) %>%
  merge(., total_replacement) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, FC, IF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  ggplot(aes(x = FC, y = IF, fill = avg_percentage)) +
  geom_tile() + labs(title = "percentage at generation 50, with NO drive (haploid fc)")

allele_replacement %>%
  filter(Allele == "C", numPartners == "D no drive") %>%
  filter(Generation == 50) %>%
  merge(., total_replacement) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, FC, IF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  ggplot(aes(x = FC, y = IF, fill = avg_percentage)) +
  geom_tile() + labs(title = "percentage at generation 50, with NO drive (diploid fc)")

## difference in fixation time
#allele_replacement %>%
#  filter(Allele == "C") %>%
#  merge(., total_replacement) %>%
#  mutate(percentage = Allele_Count / (2*Count)) %>%
#  filter(percentage == 1) %>%
#  group_by(FC, IF, numPartners, Allele, Run) %>%
#  summarise(min_gen = min(Generation)) %>%
#  group_by(FC, IF, numPartners, Allele) %>%
#  summarise(avg_generation = mean(min_gen)) %>%
#  pivot_wider(names_from = numPartners, values_from = avg_generation) %>%
#  mutate(Difference = `no drive` - `drive`) %>%
#  ggplot(aes(x=fitCost, y=introFreq, fill= Difference)) + 
#  geom_tile() +
#  labs(title = "difference in fixation time, no drive - drive")

allele_replacement %>%
  filter(IF == 0.3) %>%
  filter(FC < -0.5) %>%
  merge(., total_replacement) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, FC, IF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  filter(avg_percentage != 0) %>%
  ggplot(aes(x = Generation, y = avg_percentage, group = FC, color = FC,
             fill = FC)) +
  geom_line(size = 0.8) +
  scale_linetype_binned() +
  facet_grid(Allele~numPartners)

allele_replacement %>% 
  filter(Allele == "C", numPartners %in% c("D no drive", "drive")) %>%
  filter(Generation == 50) %>%
  merge(., total_replacement) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, FC, IF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  pivot_wider(names_from = numPartners, values_from = avg_percentage) %>%
  mutate(Difference = `drive` - `D no drive`) %>%
  ggplot(aes(x = FC, y = IF, fill = Difference)) +
  geom_tile() + labs(title = "difference in drive and no drive")

allele_replacement %>% 
  filter(Allele == "C", numPartners %in% c("D no drive", "drive")) %>%
  filter(FC == -0.3, IF == 0.05) %>%
  merge(., total_replacement) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, FC, IF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  ggplot(aes(x = Generation, y = avg_percentage, color = numPartners)) +
  geom_line(size = 0.8) + ylim(0, NA) +
  labs(title = "5% intro frequency, fitness benefit 30%")


allele_replacement %>% 
  filter(Allele == "C", numPartners %in% c("D no drive", "drive")) %>%
  filter(FC == -0.1, IF == 0.05) %>%
  merge(., total_replacement) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, FC, IF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  ggplot(aes(x = Generation, y = avg_percentage, color = numPartners)) +
  geom_line(size = 0.8) + ylim(0, NA) +
  labs(title = "5% intro frequency, fitness benefit 10%")

allele_replacement %>%
  filter(numPartners == "D no drive") %>%
  filter(FC == -0.3, IF == 0.05) %>%
  merge(., total_replacement) %>%
  mutate(percentage = Allele_Count / (2*Count)) %>%
  group_by(Generation, FC, IF, numPartners, Allele) %>%
  summarise(avg_percentage = mean(percentage)) %>%
  ggplot(aes(x = Generation, y = avg_percentage, color = numPartners)) +
  geom_line(size = 0.8) + ylim(0, NA) +
  facet_wrap(~Allele)
```



Graphing stuff - stolen from W&S heatmaps
```{r}
heatmap4_raw <- read.csv("alleleSail_data/10-31/EvI_fb/last_gen_O.csv") %>%
  mutate(type = "germline")

heatmap4_raw_som <- rbind(heatmap4_raw_som, heatmap4_raw_mc, heatmap4_raw, heatmap4_raw_gmc)

heatmap4_processed_som <- heatmap4_raw_som %>%
  group_by(introFreq, fitCost, run, type) %>%
  summarise(O_count = sum(Count),
            totalPop = sum(totalPop)) %>%
  mutate(percent_o = O_count/totalPop) %>%
  group_by(introFreq, fitCost, type) %>%
  summarise(`Avg. % Homozygous` = 1-mean(percent_o)) %>%
  ungroup()

heatmap4_processed_som %>%
  filter(!(fitCost == 0), !(type == "somatic")) %>%
  pivot_wider(names_from = type, values_from = `Avg. % Homozygous`) %>%
  mutate(Difference = `somatic mc` - `germline`) %>%
  ggplot(aes(x=fitCost, y=introFreq, fill= Difference)) + 
  geom_tile() +
  scale_fill_viridis(direction = -1) +
  labs(title = "Average % of homozygous edited individuals, difference of Somatic mc & germline") +
  xlim(NA, 0.1)
```

