---
title: "figure creation"
author: "Michelle Johnson"
date: "2024-02-09"
output:
  pdf_document: default
  html_document: default
---

Document for generating figures used in arabidopsis plant ClvR paper.

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, fig.height = 2.5)
library(tidyverse)
library(readr)
library(ggpubr)
library(scales)

options(dplyr.summarise.inform = FALSE)
options(tidyverse.quiet = TRUE)
```

## Background Functions

Basic/Helper Functions

```{r, eval=TRUE}
cbFun <- c("#ff107f", "#66b9e8", "#117733", "#c77cff", "#f2b822", "#FFEA7C")

null_plot <- ggplot() + theme_void()

windowsFonts("Arial" = windowsFont("Arial"))

getAdultData <- function(fileName){
  full_name = paste(fileName, "_adults.csv", sep = "")
  read.csv(full_name) %>%
    select(-X) %>%
    filter(Generation != "Generation") %>%
    transform(Count = as.numeric(Count), Generation = as.numeric(Generation))
}

getAlleleData <- function(fileName){
  full_name = paste(fileName, "_allele.csv", sep = "")
  read.csv(full_name) %>%
    select(-X) %>%
    filter(Generation != "Generation") %>%
    transform(Count = as.numeric(Count), Generation = as.numeric(Generation))
}

getTotalData <- function(fileName){
  full_name = paste(fileName, "_total.csv", sep = "")
  read.csv(full_name) %>%
    select(-X) %>%
    filter(Generation != "Generation") %>%
    transform(Count = as.numeric(Count), Generation = as.numeric(Generation))
}

clean_replacement <- function(dataset, number_partners) {
  dataset %>%
    separate(Run, c(NA, NA, "mcProb", NA, "fitCost", "Run"), sep = "_", remove = T) %>%
    mutate(numPartners = number_partners)
} 

clean_sterility <- function(dataset, number_partners) {
  dataset %>%
    separate(Run, c(NA, NA, "mcProb", NA, "fitCost", "Run"), sep = "_", remove = T) %>%
    mutate(numPartners = number_partners)
} 
```

Allele Functions

```{r}
get_replacement_data <- function(oneP_fn, fiveP_fn, twentyP_fn){
  # get total data for each type
  total_replacement_one <- getTotalData(oneP_fn) %>% clean_replacement(., number_partners = 1)
  total_replacement_five <- getTotalData(fiveP_fn) %>% clean_replacement(., number_partners = 5)
  total_replacement_twenty <- getTotalData(twentyP_fn) %>% clean_replacement(., number_partners = 20)
  # combine total data and make sexless
  total_replacement <- rbind(total_replacement_one, total_replacement_five, total_replacement_twenty) %>%
    group_by(Generation, fitCost, mcProb, Run, numPartners) %>%
    summarise(Count = sum(Count))
  
  #get allele data for each type
  allele_replacement_one <- getAlleleData(oneP_fn) %>% clean_replacement(number_partners = 1)
  allele_replacement_five <- getAlleleData(fiveP_fn) %>% clean_replacement(number_partners = 5)
  allele_replacement_twenty <- getAlleleData(twentyP_fn) %>% clean_replacement(number_partners = 20)
  # combine allele data and make sexless
  allele_replacement <- rbind(allele_replacement_one, allele_replacement_five, allele_replacement_twenty) %>% 
    group_by(Generation, fitCost, mcProb, Allele, Run, numPartners) %>%
    summarise(Allele_Count = sum(Count))
  
  merge(total_replacement, allele_replacement)
}

plot_replacement_panels <- function(dataset, plot_allele, y_label, top_label = FALSE, legend = TRUE) {
  plot <- dataset %>%
    filter(Allele == plot_allele) %>%
    mutate(percentage = Allele_Count / (2*Count)) %>%
    group_by(Generation, fitCost, mcProb, numPartners) %>%
    summarise(avg_percentage = mean(percentage)) %>%
    ggplot(aes(x = Generation, y = avg_percentage, color = fitCost, linetype = mcProb)) +
    geom_line(linewidth = 0.8) +
    facet_wrap(~numPartners,
               labeller = as_labeller(c(`1` = "One Partner",
                                        `5` = "Five Partners",
                                        `20` = "Twenty Partners"))) +
    labs(y = y_label,
         color = "Fitness Cost",
         linetype = "Maternal \nCarryover") +
    scale_colour_manual(values = cbFun) +
    theme_light() +
    theme(strip.text.x = element_text(size=12, color = "black", hjust = 0, face = "bold"),
          strip.background = element_rect(fill="white", size=1, color="white"))
  
  if(top_label == FALSE)plot <- plot + theme(strip.text.x = element_blank())
  
  if(legend == FALSE)plot <- plot + theme(legend.position = "none")
  
  plot
}


plot_replacement_panels_noMC <- function(dataset, plot_allele, y_label, labels = c("", "", ""), top_label = FALSE, legend = TRUE) {
  if(top_label)labels <- paste(c("One Partner\n", "Five Partners\n", "Twenty Partners\n"), labels)
  if(!("mcProb" %in% colnames(dataset))) dataset <- mutate(dataset, mcProb = 0)
  
  plot <- dataset %>%
    filter(Allele == plot_allele, mcProb == 0) %>%
    mutate(percentage = Allele_Count / (2*Count)) %>%
    group_by(Generation, fitCost, numPartners) %>%
    summarise(avg_percentage = mean(percentage)) %>%
    ggplot(aes(x = Generation, y = avg_percentage, color = fitCost)) +
    geom_line(linewidth = 0.8) +
    facet_wrap(~numPartners,
               labeller = as_labeller(c(`1` = labels[1], #"One Partner",
                                        `5` = labels[2], #"Five Partners",
                                        `20` = labels[3]))) + #"Twenty Partners"))) +
    labs(y = y_label,
         color = "Fitness Cost") +
    scale_colour_manual(values = cbFun) +
    theme_light() +
    theme(strip.text.x = element_text(size=12, color = "black", hjust = 0, face = "bold"),
          strip.background = element_blank(), #element_rect(fill="white", size=0, color="white", alpha = 0),
          panel.spacing = unit(8, "pt"))
  
  if(legend == FALSE)plot <- plot + theme(legend.position = "none")
  
  plot
}
```

Total Population Functions

```{r}
get_suppression_data <- function(oneP_fn, fiveP_fn, twentyP_fn){
  # collect all the data
  total_fsterile_one <- getTotalData(oneP_fn) %>%
    clean_sterility(., number_partners = 1)
  
  total_fsterile_five <- getTotalData(fiveP_fn) %>%
    clean_sterility(., number_partners = 5)
  
  total_fsterile_twenty <- getTotalData(twentyP_fn) %>%
    clean_sterility(., number_partners = 20)
  
  total_fsterile <- rbind(total_fsterile_one, total_fsterile_five) %>%
    rbind(., total_fsterile_twenty) %>%
    group_by(Generation, Run, mcProb, fitCost, numPartners) %>%
    summarise(Count = sum(Count))
}

plot_suppression_data <- function(dataset, labels = c("", "", ""), top_label = FALSE){
  if(top_label)labels <- paste(c("One Partner\n", "Five Partners\n", "Twenty Partners\n"), labels)
  
  female_plot <- dataset %>%
    filter(fitCost != 0.2) %>%
    #filter(mcProb %in% c(0, 0.3, 1.0)) %>%
    group_by(Generation, mcProb, fitCost, numPartners) %>%
    summarise(avg_Count = mean(Count)) %>% # remove Runs
    ggplot(aes(x = Generation, y = avg_Count, group = paste(fitCost, mcProb), color = fitCost, linetype = mcProb)) +
    geom_line(linewidth =0.8) +
    facet_wrap(~numPartners, ncol = 3,
               labeller = as_labeller(c(`1` = labels[1],
                                        `5` = labels[2],
                                        `20` = labels[3]))) +
    labs(y = "Average Total Population",
         color = "Fitness Cost", 
         linetype = "Maternal \nCarryover") +
    #ylim(0, 10000) +
    scale_y_continuous(breaks=c(0, 2500, 5000, 7500, 10000)) +
    theme_light() +
    #xlim(0, 30) +
    scale_colour_manual(values = cbFun)
    
  female_plot <- female_plot +
    theme(strip.text.x = element_text(size=12, color = "black", hjust = 0, face = "bold"),
          strip.background = element_blank(), #element_rect(fill="white", size=0, color="white", alpha = 0),
          panel.spacing = unit(8, "pt")) #,
      #strip.text.x = element_text(angle = 0, hjust = 0),
      #text = element_text(size = 10, family = "Arial"))
  
  female_plot
}

plot_suppression_runwise <- function(dataset, labels = c("", "", ""), top_label = FALSE){
  if(top_label)labels <- paste(c("One Partner\n", "Five Partners\n", "Twenty Partners\n"), labels)
  
  dataset <- dataset %>%
    filter(fitCost != 0.2) #, mcProb %in% c(0, 0.3))
  
  dataset_oneP <- dataset %>% filter(numPartners == 1)
  dataset_multiP <- dataset %>% filter(numPartners > 1)
  
  avg_dataset <- dataset %>%
    group_by(Generation, mcProb, fitCost, numPartners) %>%
    summarize(Count = mean(Count)) %>%
    ungroup()
  
  female_plot <- dataset_oneP %>%
    ggplot(aes(x = Generation, y = Count, group = paste(fitCost, mcProb, Run), color = fitCost, linetype = mcProb)) +
    geom_line(linewidth = 0.6, alpha = 0.35) +
    geom_line(data = dataset_multiP, linewidth = 0.5, alpha = 0.2) +
    geom_line(data = avg_dataset, linewidth = 1, 
              aes(group = paste(fitCost, mcProb))) +
    facet_wrap(~numPartners, ncol = 3,
               labeller = as_labeller(c(`1` = labels[1],
                                        `5` = labels[2],
                                        `20` = labels[3]))) +
    labs(y = "Average Total Population",
         color = "Fitness Cost", 
         linetype = "Maternal \nCarryover") +
    ylim(0, 10000) +
    scale_y_continuous(breaks=c(0, 2500, 5000, 7500, 10000)) +
    theme_light() +
    scale_colour_manual(values = cbFun)
  
  female_plot <- female_plot +
    theme(strip.text.x = element_text(size=12, color = "black", hjust = 0, face = "bold"),
          strip.background = element_blank(), #element_rect(fill="white", size=0, color="white", alpha = 0),
          panel.spacing = unit(8, "pt"))
}
```


## No Mutations

Figure 5: 10% Introduction Frequency

```{r, fig.height = 7, fig.width = 8}
fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")

tenPercent_replacement <- get_replacement_data("arabidopsis_data/haploidFitCosts_int10_onePartner_noSterile",
                     "arabidopsis_data/haploidFitCosts_int10_fivePartner_noSterile",
                     "arabidopsis_data/haploidFitCosts_int10_twentyPartner_noSterile") %>% filter(fitCost < 0.2) %>%
    plot_replacement_panels_noMC("V", "Percent ClvR", labels = c("a", "b", "c"), legend = FALSE, top_label = TRUE)

#'atop(bold("This should be bold"),"this should not")'

tenPercent_femSterile <- get_suppression_data("arabidopsis_data/sterile_females_int10_onePartner2",
                     "arabidopsis_data/sterile_females_int10_fivePartner2",
                     "arabidopsis_data/sterile_females_int10_twentyPartner2") %>%
  filter(mcProb < 0.5) %>% 
  plot_suppression_data(labels = c("d", "e", "f"))

tenPercent_maleSterile <- get_suppression_data("arabidopsis_data/sterile_males_int10_onePartner2",
                     "arabidopsis_data/sterile_males_int10_fivePartner2",
                     "arabidopsis_data/sterile_males_int10_twentyPartner2") %>% 
  filter(mcProb < 0.5) %>% 
  plot_suppression_data(labels = c("g", "h", "i")) +
  theme(legend.position = "none")

fig <- ggarrange(null_plot,
                 tenPercent_replacement, 
                 null_plot,
                 tenPercent_femSterile + theme(legend.position = "none"),
                 null_plot,
                 tenPercent_maleSterile,
          nrow = 6, 
          labels = c("Replacement", "",
                     "Suppression: Females Sterile", "",
                     "Suppression: Males Sterile", ""),
          heights = c(0.12, 1.1, 0.12, 1, 0.12, 1),
          hjust = 0) %>%
  annotate_figure(fig.lab = "10% introduction frequency", top = " ")


fig1 <- ggarrange(fig, as_ggplot(get_legend(tenPercent_femSterile)),
                  widths = c(5, 1))
fig1

ggsave("final_figures/Figure_5.svg", plot = fig1,
       height = fig_height, width = fig_width)
ggsave("final_figures/Figure_5.png", plot = fig1,
       height = fig_height, width = fig_width, bg = "white")
```

Supplemental Figure, 10% introduction frequency suppression with maternal carryover 1

```{r, fig.height = 5, fig.width = 8}
fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")

tenPercent_femSterile_s <- get_suppression_data("arabidopsis_data/sterile_females_int10_onePartner2",
                     "arabidopsis_data/sterile_females_int10_fivePartner2",
                     "arabidopsis_data/sterile_females_int10_twentyPartner2") %>%
  plot_suppression_data(labels = c("a", "b", "c"), top_label = TRUE)

tenPercent_maleSterile_s <- get_suppression_data("arabidopsis_data/sterile_males_int10_onePartner2",
                     "arabidopsis_data/sterile_males_int10_fivePartner2",
                     "arabidopsis_data/sterile_males_int10_twentyPartner2") %>% 
  plot_suppression_data(labels = c("d", "e", "f")) +
  theme(legend.position = "none")

fig <- ggarrange(null_plot,
                 tenPercent_femSterile_s + theme(legend.position = "none"),
                 null_plot,
                 tenPercent_maleSterile_s,
          nrow = 4, 
          labels = c("Suppression: Females Sterile", "",
                     "Suppression: Males Sterile", ""),
          heights = c(0.12, 1.1, 0.12, 1, 0.12, 1),
          hjust = 0) %>%
  annotate_figure(fig.lab = "10% introduction frequency", top = " ")


fig1s <- ggarrange(fig, as_ggplot(get_legend(tenPercent_femSterile_s)),
                  widths = c(5, 1))
fig1s

ggsave("final_figures/X_Figure_8-MC1_fig_5.svg", plot = fig1s,
       height = fig_height, width = fig_width)
ggsave("final_figures/X_Figure_8-MC1_fig_5.png", plot = fig1s,
       height = fig_height, width = fig_width, bg = "white")
```


Supplemental Figure, 20% Introduction Frequency

```{r, fig.height = 7, fig.width = 8}
fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")

twentyPercent_replacement <- get_replacement_data("arabidopsis_data/haploidFitCosts_int20_onePartner_noSterile",
                     "arabidopsis_data/haploidFitCosts_int20_fivePartner_noSterile",
                     "arabidopsis_data/haploidFitCosts_int20_twentyPartner_noSterile") %>%filter(fitCost < 0.2) %>%
    plot_replacement_panels_noMC("V", "Percent ClvR", labels = c("a", "b", "c"), legend = FALSE, top_label = TRUE)

twentyPercent_femSterile <- get_suppression_data("arabidopsis_data/sterile_females_int20_onePartner",
                     "arabidopsis_data/sterile_females_int20_fivePartner",
                     "arabidopsis_data/sterile_females_int20_twentyPartner") %>% plot_suppression_data(labels = c("d", "e", "f"))

twentyPercent_maleSterile <- get_suppression_data("arabidopsis_data/sterile_males_int20_onePartner",
                     "arabidopsis_data/sterile_males_int20_fivePartner",
                     "arabidopsis_data/sterile_males_int20_twentyPartner") %>% plot_suppression_data(labels = c("g", "h", "i")) +
  theme(legend.position = "none")

fig <- ggarrange(null_plot,
                 twentyPercent_replacement, 
                 null_plot,
                 twentyPercent_femSterile + theme(legend.position = "none"),
                 null_plot,
                 twentyPercent_maleSterile,
          nrow = 6, 
          labels = c("Replacement", "",
                     "Suppression: Females Sterile", "",
                     "Suppression: Males Sterile", ""),
          heights = c(0.12, 1.1, 0.12, 1, 0.12, 1),
          hjust = 0) %>%
  annotate_figure(fig.lab = "20% introduction frequency", top = " ")
fig

fig2 <- ggarrange(fig, as_ggplot(get_legend(twentyPercent_femSterile)),
                  widths = c(5, 1))
fig2

ggsave("final_figures/X_Figure_7-20percent_fig_5.svg", plot = fig2,
       height = 7, width = 8) #fig_height, width = fig_width)
ggsave("final_figures/X_Figure_7-20percent_fig_5.png", plot = fig2,
       height = 7, width = 8, bg = "white") #fig_height, width = fig_width)
```



## RD and LOF

Figure 6: Recombination Distance and Loss of Function Cas9 (1% of 10%), for population modification

```{r, fig.height=9, fig.width=8}

fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")

# set up recombination distance

RD_set <- get_replacement_data("arabidopsis_data/rd_1_modification_onePartner",
                               "arabidopsis_data/rd_1_modification_fivePartner",
                               "arabidopsis_data/rd_1_modification_twentyPartner")

rd_rescue <- plot_replacement_panels_noMC(RD_set, "R", "\nPercent Rescue/Cargo/gRNAs", legend = FALSE, top_label = TRUE)

rd_cas9 <- plot_replacement_panels_noMC(RD_set, "V", "\nPercent Cas9")

rd_combo <- ggarrange(rd_rescue, rd_cas9 + theme(legend.position = "none"), nrow = 2, heights = c(1.1, 1), labels = c("a", "b"))

# set up loss-of-function

LOF_set <- get_replacement_data("arabidopsis_data/lof_modification_if1_fs_onePartner",
                                "arabidopsis_data/lof_modification_if1_fs_fivePartner",
                                "arabidopsis_data/lof_modification_if1_fs_twentyPartner")

LOF_fullClvr <- LOF_set %>%
  filter(Allele %in% c("V", "R")) %>%
  mutate(Allele = "V") %>%
  group_by(Generation, fitCost, mcProb, Run, numPartners, Allele) %>%
  summarize(Allele_Count = sum(Allele_Count),
            Count = min(Count)) # Count should be the same for both, so Count just gets to be Count

LOF_cas9 <- plot_replacement_panels_noMC(LOF_fullClvr, "V", "Percent ClvR\n(including Rescue-Only", legend = FALSE)

LOF_rescue <- plot_replacement_panels_noMC(LOF_set, "V", "Functioning ClvR\n(not including Rescue-Only)", legend = FALSE)

LOF_combo <- ggarrange(LOF_cas9, LOF_rescue, nrow = 2, heights = c(1.1, 1), labels = c("c", "d"))

# arrange and save

fig <- ggarrange(null_plot,
                 rd_combo, 
                 null_plot,
                 LOF_combo,
                 nrow = 4,
          labels = c("Recombination Distance", "", "Loss of Function Cas9, 1% of 10%", ""),
          heights = c(0.06, 1.05, 0.08, 1), hjust=0)

fig <- ggarrange(fig, as_ggplot(get_legend(rd_cas9)), ncol = 2, widths = c(5, 1))

fig

ggsave("RD_LOF_mod_i1.svg", plot = fig,
       height = fig_height, width = fig_width, bg = "white")
ggsave("RD_LOF_mod_i1.png", plot = fig,
       height = fig_height, width = fig_width, bg = "white")
```


Figure 6: Recombination Distance and Loss of Function Cas9 (20% of 10%), for population modification

```{r, fig.height=9, fig.width=8}

fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")

# set up recombination distance

RD_set <- get_replacement_data("arabidopsis_data/rd_1_modification_onePartner",
                               "arabidopsis_data/rd_1_modification_fivePartner",
                               "arabidopsis_data/rd_1_modification_twentyPartner")

rd_rescue <- plot_replacement_panels_noMC(RD_set, "R", "\nPercent Rescue/Cargo/gRNAs", legend = FALSE, top_label = TRUE)

rd_cas9 <- plot_replacement_panels_noMC(RD_set, "V", "\nPercent Cas9")

rd_combo <- ggarrange(rd_rescue, rd_cas9 + theme(legend.position = "none"), nrow = 2, heights = c(1.1, 1), labels = c("a", "b"))

# set up loss-of-function

LOF_set <- get_replacement_data("arabidopsis_data/lof_modification_if1_fs_onePartner",
                                "arabidopsis_data/lof_modification_if1_fs_fivePartner",
                                "arabidopsis_data/lof_modification_if1_fs_twentyPartner")

LOF_fullClvr <- LOF_set %>%
  filter(Allele %in% c("V", "R")) %>%
  mutate(Allele = "V") %>%
  group_by(Generation, fitCost, mcProb, Run, numPartners, Allele) %>%
  summarize(Allele_Count = sum(Allele_Count),
            Count = min(Count)) # Count should be the same for both, so Count just gets to be Count

LOF_cas9 <- plot_replacement_panels_noMC(LOF_fullClvr, "V", "Percent ClvR\n(including Rescue-Only", legend = FALSE)

LOF_rescue <- plot_replacement_panels_noMC(LOF_set, "V", "Functioning ClvR\n(not including Rescue-Only)", legend = FALSE)

LOF_combo <- ggarrange(LOF_cas9, LOF_rescue, nrow = 2, heights = c(1.1, 1), labels = c("c", "d"))

# arrange and save

fig <- ggarrange(null_plot,
                 rd_combo, 
                 null_plot,
                 LOF_combo,
                 nrow = 4,
          labels = c("Recombination Distance", "", "Loss of Function Cas9, 1% of 10%", ""),
          heights = c(0.06, 1.05, 0.08, 1), hjust=0)

fig <- ggarrange(fig, as_ggplot(get_legend(rd_cas9)), ncol = 2, widths = c(5, 1))

fig

ggsave("final_figures/Figure_6-RD_LOF_modification_i20.svg", plot = fig,
       height = fig_height, width = fig_width, bg = "white")
ggsave("final_figures/Figure_6-RD_LOF_modification_i20.png", plot = fig,
       height = fig_height, width = fig_width, bg = "white")
```

### Suppression

Figure 7: Just Loss of Function, 1% of 10%

```{r, fig.height=2.5, fig.width=8}

fig_height = 5
fig_width = 8

fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")

LOF_sup <- get_suppression_data("arabidopsis_data/lof_suppression_if1_fs_onePartner",
                                "arabidopsis_data/lof_suppression_if1_fs_fivePartner",
                                "arabidopsis_data/lof_suppression_if1_fs_twentyPartner") %>% 
  plot_suppression_data(top_label = TRUE)

fig <- ggarrange(LOF_sup + theme(legend.position = "none"), as_ggplot(get_legend(LOF_sup)), ncol = 2, widths = c(5, 1)) %>%
  annotate_figure(fig.lab = "Loss of Function Cas9, 1% of 10%",
                  top = " ")

fig

ggsave("final_figures/Figure_7-LOF_if1_suppression.svg", plot = fig,
       height = fig_height, width = fig_width, bg = "white")
ggsave("final_figures/Figure_7-LOF_if1_suppression.png", plot = fig,
       height = fig_height, width = fig_width, bg = "white")

```

Supplemental Figure, Suppression for Recombination Distance and 20% of 10% Loss of Function

```{r, fig.height=5, fig.width=8}

fig_height = 5
fig_width = 8

fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")

LOF_sup <- get_suppression_data("arabidopsis_data/lof_suppression_if20_fs_onePartner",
                                "arabidopsis_data/lof_suppression_if20_fs_fivePartner",
                                "arabidopsis_data/lof_suppression_if20_fs_twentyPartner") %>% 
  plot_suppression_runwise(top_label = TRUE)

rd_sup <- get_suppression_data("arabidopsis_data/rd_1_suppression_fs_onePartner",
                               "arabidopsis_data/rd_1_suppression_fs_fivePartner",
                               "arabidopsis_data/rd_1_suppression_fs_twentyPartner") %>% 
  plot_suppression_runwise() +
  theme(legend.position = "none")

fig <- ggarrange(null_plot, 
                 annotate_figure(LOF_sup + theme(legend.position = "none"), fig.lab = "a", fig.lab.face = "bold"),
                 null_plot,
                 annotate_figure(rd_sup, fig.lab = "b", fig.lab.face = "bold"),
          nrow = 4,
          labels = c("Loss of Function Cas9, 20% of 10%", "", "Recombination Distance", ""),
          heights = c(0.15, 1.1, 0.15, 1), hjust=0)

fig <- ggarrange(fig, as_ggplot(get_legend(LOF_sup)), ncol = 2, widths = c(5, 1))

fig

ggsave("final_figures/X_Figure_9-LOF_RD_suppression.svg", plot = fig,
       height = fig_height, width = fig_width, bg = "white")
ggsave("final_figures/X_Figure_9-LOF_RD_suppression.png", plot = fig,
       height = fig_height, width = fig_width, bg = "white")
```



## Resistant Mutations

### Modification

10% standing resistance (5% allele)

```{r, fig.height=4, fig.width=8}

fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")

# set up recombination distance

Res_mod <- get_replacement_data("arabidopsis_data/resistant_modification_heterozygotes_int10_onePartner",
                               "arabidopsis_data/resistant_modification_heterozygotes_int10_fivePartner",
                               "arabidopsis_data/resistant_modification_heterozygotes_int10_twentyPartner") %>%
  filter(fitCost < 0.2)

res_cas9 <- plot_replacement_panels_noMC(Res_mod, "V", "\nPercent ClvR", top_label = TRUE, legend = FALSE)

res_res <- plot_replacement_panels_noMC(Res_mod, "R", "\nPercent Resistant", legend = TRUE)

res_combo <- ggarrange(null_plot, res_cas9, res_res + theme(legend.position = "none"), nrow = 3, heights = c(0.1, 1.1, 1), labels = c("", "a", "b")) %>%
  annotate_figure(fig.lab = "Resistant Mutation & Replacement, 10%")

fig <- ggarrange(res_combo, as_ggplot(get_legend(res_res)), ncol = 2, widths = c(5, 1))

```


2% standing resistance (1% allele)

```{r, fig.height=4, fig.width=8}

fig_height = 4
fig_width = 8

fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")

Res_mod <- get_replacement_data("arabidopsis_data/resistant_modification_heterozygotes_int2_onePartner",
                               "arabidopsis_data/resistant_modification_heterozygotes_int2_fivePartner",
                               "arabidopsis_data/resistant_modification_heterozygotes_int2_twentyPartner") %>%
  filter(fitCost < 0.2)

res_cas9 <- plot_replacement_panels_noMC(Res_mod, "V", "\nPercent ClvR", top_label = TRUE, legend = FALSE)

res_res <- plot_replacement_panels_noMC(Res_mod, "R", "\nPercent Resistant", legend = TRUE)

res_combo <- ggarrange(null_plot, res_cas9, res_res + theme(legend.position = "none"), nrow = 3, heights = c(0.1, 1.1, 1), labels = c("", "a", "b")) %>%
  annotate_figure(fig.lab = "Resistant Mutation & Replacement, 2%")

fig2 <- ggarrange(res_combo, as_ggplot(get_legend(res_res)), ncol = 2, widths = c(5, 1))

```


### Suppression

```{r, fig.height = 7, fig.width = 4}

fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")
fig_height = 7
fig_width = 4

RS_total <- getTotalData("arabidopsis_data/resistant_suppression_into0001percent_int10_fs_onePartner") %>%
  clean_sterility(number_partners = 1) %>%
  group_by(Generation, fitCost, mcProb, Run, numPartners) %>%
    summarise(Count = sum(Count))
  
RS_allele <- getAlleleData("arabidopsis_data/resistant_suppression_into0001percent_int10_fs_onePartner") %>%
  clean_sterility(number_partners = 1) %>%
    group_by(Generation, fitCost, mcProb, Allele, Run, numPartners) %>%
    summarise(Allele_Count = sum(Count))

RS_adult <- getAdultData("arabidopsis_data/resistant_suppression_into0001percent_int10_fs_onePartner") %>%
  clean_sterility(number_partners = 1) %>%
    group_by(Generation, fitCost, mcProb, Genotype, Run, numPartners) %>%
    summarise(Count = sum(Count))

RS_data <- merge(RS_total, RS_allele) %>%
  mutate(percent = Allele_Count / (Count * 2))

linear <- RS_data %>% 
  mutate(Count2 = Count / 10^7) %>%
  ggplot(aes(x = Generation, y = Count2, group = Run)) +
  geom_line() +
  labs(y = "Total Population",
       title = "Linear scale") +
  theme_light() +
  scale_y_continuous(labels = label_math(.x %*% 10^7))

logarithmic <- RS_data %>% ggplot(aes(x = Generation, y = Count, group = Run)) +
  geom_line() +
  labs(y = "Total Population",
       title = "Log scale") +
  theme_light() +
  scale_y_continuous(trans = 'log10', 
                     breaks = trans_breaks('log10', function(x) 10^x),
                     labels = trans_format('log10', math_format(10^.x)))

rs_alleles <- RS_data %>% 
  group_by(Generation, Allele) %>%
  summarize(Frequency = mean(percent)) %>%
  ggplot(aes(x = Generation, y = Frequency, color = Allele)) +
  geom_line(linewidth = 0.8) +
  labs(y = "Allele Frequency",
       title = "Allele Frequencies") +
  theme_light() +
  scale_color_manual(limits = c("A", "C", "R", "V", "W"),
    labels = c("Target Cleavable\n Allele", "Cleaved Alleles", "Cleavage-Resistant\n Allele", "ClvR", "Non-ClvR"),
    values = cbFun) +
  guides(color = guide_legend(override.aes = list(linewidth = 1)))

panel <- ggarrange(linear, logarithmic, rs_alleles, nrow = 3) %>%
  annotate_figure(fig.lab = "Suppression with 100/100,000,000 resistant individuals", top = " ")

```


### Combine Modification and Suppression

```{r, fig.height=6, fig.width=8}
fig_height = 6
fig_width = 8
fig_height = knitr::opts_current$get("fig.height")
fig_width = knitr::opts_current$get("fig.width")

res_combo <- ggarrange(null_plot, res_cas9, res_res + theme(legend.position = "none"), null_plot,
                       nrow = 4, heights = c(0.1, 1.1, 1, 0.1), labels = c("", "a", "b", "")) %>%
  annotate_figure(fig.lab = "Modification with 200 / 10,000 resistant individuals")

resmod_panel <- ggarrange(res_combo, as_ggplot(get_legend(res_res)), ncol = 2, widths = c(5, 1.5))

rs_alleles2 <- RS_data %>% 
  group_by(Generation, Allele) %>%
  summarize(Frequency = mean(percent)) %>%
  ggplot(aes(x = Generation, y = Frequency, color = Allele)) +
  geom_line(linewidth = 0.8) +
  labs(y = "Allele Frequency",
       title = "Allele Frequencies") +
  theme_light() +
  scale_color_manual(limits = c("A", "C", "R", "V", "W"),
    labels = c("Target Cleavable Allele", "Cleaved Alleles", "Cleavage-Resistant Allele", "ClvR", "Non-ClvR"),
    values = cbFun) +
  guides(color = guide_legend(override.aes = list(linewidth = 1))) +
  theme(legend.position = "bottom",
        legend.justification = "right")

title_size <- 10

ressup <- ggarrange(linear + theme(plot.title = element_text(size=title_size)),
                              logarithmic + theme(plot.title = element_text(size=title_size)),
                              rs_alleles + theme(legend.position = "none",
                                                 plot.title = element_text(size=title_size)), ncol = 3)
                              #labels = c("c", "", "")) %>%

ressup_panel1 <- ggarrange(ressup, as_ggplot(get_legend(rs_alleles)), ncol = 2, widths = c(5, 1.5))

ressup_panel <- ggarrange(null_plot, ressup_panel1, nrow = 2, heights = c(0.13, 1),
                          labels = c("c", "")) %>% 
  annotate_figure(fig.lab = "Suppression with 100/100,000,000 resistant individuals", top = " ", )

resistance_mod_sup <- ggarrange(resmod_panel,
          annotate_figure(null_plot,
                          fig.lab = "Suppression with 100/100,000,000 resistant individuals"),
                                            # hjust = 1.1, size = 10)), 
          ressup_panel1, 
          nrow = 3, heights = c(2,0.17, 1), labels = c("", "c", "")) %>%
  annotate_figure(fig.lab = "Resistance mutation", top = " ")
  
#resistance_mod_sup

#ggsave("res_modAndSuppression_int10_mod.svg", plot = resistance_mod_sup,
#       height = fig_height, width = fig_width, bg = "white")
#ggsave("res_modAndSuppression_int10_mod.png", plot = resistance_mod_sup,
#       height = fig_height, width = fig_width, bg = "white")
```

```{r, fig.height=6, fig.width=8}
ressup <- ggarrange(linear + theme(plot.title = element_text(size=title_size)),
                              logarithmic + theme(plot.title = element_text(size=title_size)),
                              rs_alleles + theme(legend.position = "none",
                                                 plot.title = element_text(size=title_size)), ncol = 3)

ressup <- ggarrange(null_plot, ressup, nrow = 2,
                    heights = c(0.2, 1),
                    labels = c("c", ""))

ressup_panel1 <- ggarrange(ressup, as_ggplot(get_legend(rs_alleles)), ncol = 2, widths = c(5, 1.5))

res_combo2 <- ggarrange(null_plot, res_cas9, res_res + theme(legend.position = "none"), null_plot,
                       nrow = 4, heights = c(0.1, 1.1, 1, 0.1), labels = c("", "a", "b", "")) %>%
  annotate_figure(fig.lab = " ", fig.lab.face = "bold")

resmod_panel2 <- ggarrange(res_combo2, as_ggplot(get_legend(res_res)), ncol = 2, widths = c(5, 1.5))

resmodsup_bold <- ggarrange(null_plot, resmod_panel2, null_plot, #ressup,
          annotate_figure(ressup_panel1, fig.lab = " ", fig.lab.face = "bold"),
          nrow = 4,
          labels = c("Modification with a 1% frequency of resistant alleles", "",  
                     "",
                     ""), #Suppression 5x10 ^-7resistant individuals", ""),
          heights = c(0.15, 2, 0.13, 1),
          hjust = 0) +
  geom_text(aes(x=0, y=0.32, label = #'bold(10^-7)'),
                  'bold("Suppression with a 5x10"^"-7" ~ "frequency of resistant alleles")'),
            parse = TRUE, size = 4.8, hjust = 0)

resmodsup_bold

ggsave("final_figures/Figure_8-resistance_modification_suppression.svg", plot = resmodsup_bold,
       height = fig_height, width = fig_width, bg = "white")
ggsave("final_figures/Figure_8-resistance_modification_suppression.png", plot = resmodsup_bold,
       height = fig_height, width = fig_width, bg = "white")
```


## Loci Jumping

```{r, fig.height = 5, fig.width = 6}
######## Do ClvR Locus Jumping ##########

CLJ_total <- getTotalData("arabidopsis_data/JumpingClvR_intVariable_femSterile_onePartner") %>%
  separate(Run, c(NA, "intro", NA, "fitCost", "Run", NA), sep = "_", remove = T) %>%
  group_by(Generation, intro, fitCost, Run) %>%
    summarise(Count = sum(Count))

linear_CLJ <- CLJ_total %>% 
  mutate(Count2 = Count / 10^7) %>%
  ggplot(aes(x = Generation, y = Count2, group = Run)) +
  geom_line() +
  labs(y = "Total Population",
       title = "Linear scale") +
  theme_light() +
  scale_y_continuous(labels = label_math(.x %*% 10^7))

logarithmic_CLJ <- CLJ_total %>% ggplot(aes(x = Generation, y = Count, group = Run)) +
  geom_line() +
  labs(y = "Total Population",
       title = "Log scale") +
  theme_light() +
  scale_y_continuous(trans = 'log10', 
                     breaks = trans_breaks('log10', function(x) 10^x),
                     labels = trans_format('log10', math_format(10^.x)))

clj <- ggarrange(linear_CLJ, logarithmic_CLJ, ncol = 2, labels = c("a", "b"))

######## Do Fertility Jumping ##########

FJ_total <- getTotalData("arabidopsis_data/JumpingFertility_intVariable_femSterile_onePartner") %>%
  separate(Run, c(NA, "intro", NA, "fitCost", "Run", NA), sep = "_", remove = T) %>%
  group_by(Generation, intro, fitCost, Run) %>%
    summarise(Count = sum(Count))

linear_FJ <- FJ_total %>% 
  mutate(Count2 = Count / 10^7) %>%
  ggplot(aes(x = Generation, y = Count2, group = Run)) +
  geom_line() +
  labs(y = "Total Population",
       title = "Linear scale") +
  theme_light() +
  scale_y_continuous(labels = label_math(.x %*% 10^7))

logarithmic_FJ <- FJ_total %>% ggplot(aes(x = Generation, y = Count, group = Run)) +
  geom_line() +
  labs(y = "Total Population",
       title = "Log scale") +
  theme_light() +
  scale_y_continuous(trans = 'log10', 
                     breaks = trans_breaks('log10', function(x) 10^x),
                     labels = trans_format('log10', math_format(10^.x)))

fj <- ggarrange(linear_FJ, logarithmic_FJ, ncol = 2, labels = c("c", "d"))

jumping_fig <- ggarrange(null_plot, clj, null_plot, fj,
          nrow = 4, labels = c("ClvR locus transposition", "", "Fertility locus transposition", ""),
          heights = c(0.15, 1, 0.13, 1),
          hjust = 0)

jumping_fig

ggsave("final_figures/X_Figure_10-jumping_loci.svg", plot = jumping_fig,
       height = fig_height, width = fig_width, bg = "white")
ggsave("final_figures/X_Figure_10-jumping_loci.png", plot = jumping_fig,
       height = fig_height, width = fig_width, bg = "white")
```

